
\documentclass[11pt]{article}
\usepackage{hyperref}
\usepackage{graphicx}
\begin{document}
\begin{titlepage}
\centering
\vspace{4cm}
{\huge\bfseries TITLE \par}
\vspace{2cm}
{\Large\itshape Geometron\par}
\vfill
{\large \today\par}
\end{titlepage}


<a href="index.php?filename=fivebooksofgeometron.txt}back to 5 books</a>



\section{Network Cosmology}


This used to be the Book of Meaning, it is a philosophy for a networked society




What are we trying to do here?  Decide how to live.  How to exist.




We are at war with literalism, materialism, reductionism, capitalism.




Seizing back "cosmology" from our Enemies




Self-replicating fractal link/symbol networks will replace all commerce and industry.  The "tech" capitalists have started to show the power of networks to "disrupt" the existing order, but by keeping capitalism in place they have only amplified the contradictions of the existing system.




We can replace Uber, Lyft, Amazon, Facebook, the entire "gig economy" all the payment gateways, by a system of allowing energy information and materials to flow through the network, for that network to grow and evolve and replicate.  The Tech Drones speak of 




Quantum Street Jesus as a path of understanding in the so-called USA




Capitalism is a religion that forces numbers to be "real".




Scale of the network: trillions of web server instances for billions of human minds= end of property concept as possible to parse by human mind




Emergence of the "Tech Drones" as an evil, mindless AI.  History which traces back to bureaucracy from before computers, mostly via military empires and the Church, tracing back to various temple-based power structures of Axial Age and before.  This system is the enemy of all living minds which are not the System.  This is a whole section, in which we take apart the evil of computer "science" and all its horrible inhuman followers, challenge the basic humanity of Evil men like Zuckerberg and Musk.




The section on Tech Drones can be called a "history of evil".  Connect the Tech Drones with the Roman Empire, the Nazi cult, the USSR, Napoleon's military, the modern USA military, Byzantium, Holy Roman Empire, modern multinational corporations, authoritarian temples/churches.  Tech Drones are evil incarnate.  Evil is a real thing on this Earth.




A note on cybersecurity




Capitalism, and the failure of number based currency to ever solve the problems it creates: slavery reparations, landlordism, destruction of the natural world.  Hence, a shift from number to network construction.  But in order to navigate a topological network we need ICONS, and MAPS, both of which require GEOMETRY.  Hence GEOMETRON.




Meaning of things: factory, map, flow, watershed, street, hyphae, mycellium, 




Note to Marxists: Labor theory of Value doesn't deal with situations when there is no added labor to create value, i.e. automation and self replication, or a fully networked society where value comes from the nodes of a network.  Factories are no longer a building with workers, they are topological entities, with all elements replaceable, this means that classical Marxist theory is irrelevent.  Class struggle is binary, and has no topological content.  We are not in opposition to the basic tenets of Marxism for the industry that used to exist, and this alternative is not capitalism, it is something new.  It is topological and rejects not only the binary of class struggle but the basic reality of numbers as a good descriptor of our world.  




Note to Capitalists: Topological based systems for organizing society have, literally <em>more degrees of freedom</em> than numerical ones.  Thus, if you believe in the "freedom of free markets", this system offers a <em>more free</em> option, a more free market than any market you have ever heard of.  In comparison to topological mapping based society, so-called "free markets" based on reduction of all things to number-described commodities is as simple-minded and constricting as Soviet-style command economies are.  Nothing here is in contradiction to your system of free markets leading to personal freedom, it is a generalization to a much more free system, with a much greater diversity of ideas than would be possible in a numerical system.




The Nine Laws of Geometron: what each one means, how to apply it to every day life




Numerology in our system, what it means to give numbers special meaning.  Universality of symmetry based systems of meaning that move from geometric symmetry to number, not the other way around.




The Great Transofrmation




from: 


<ul>
<li>capitalism</li>
<li>property</li>
<li>money</li>
<li>ego</li>
<li>strict numerical monotheism</li>
<li>heiearchy</li>
<li>mining, fire, bury</li>
<li>Marxist theory</li>
<li>machine replication theory today: the full cartoon, with powerpoint, investors, adertising, consumers, media, mining, oil, trucking</li>
</ul>


to:


<ul>
<li>symbols for links</li>
<li>self replicating data structures</li>
<li>factories as topological data structures of actions</li>
<li>disposable servers</li>
<li>localized cosmology based on language</li>
<li>QSJ in the Christian West, equivalent in other places</li>
<li>Ego Death</li>
<li>Natural flows of things, with no specific effort by any individual, they just flow</li>
<li>"corporate structure" of us: what we will and won't do, rules to live by, eg no stock, no debt, etc etc. What we CAN do and WILL do to "make money" in order to replicate inside the existing system.  We are self replicating clay in a pre-RNA world. We will replicate and die.</li>
</ul>


A tour of all the other books and how they tie into this philosophy, how they lead to this better world we are attempting to describe: Action Geometry, Trash Robot, Map Factory, Geometron Hyperspace or Hypercube or Virtual Machine




Tie this work into future and past work: Trash Magic Manifesto, and the future work of building out the complete technological set from Trash Robot


\end{document}
